Analysis of cloud enhancement events in a 30-year record of global solar irradiance at Thessaloniki, Greece

### 2024-09-19 article/article.Rmd
Commit 2024-09-19 11:10

<!-- Radiation data quality check -->
To further improve the quality of the irradiance data, a manual screening was
performed, to remove inconsistent and erroneous recordings that can occur
stochastically or systematically during the long operation of the instrument.  The
manual screening was aided by a radiation data quality assurance procedure, adjusted
for the site, which was based on the methods of Long and Shi\ [@Long2006;
@Long2008a].  Thus, problematic recordings have been excluded from further
processing.  Furthermore, due to the significant measurement uncertainty in GHI when
the Sun is near the horizon, and due to some systematic obstructions by nearby
buildings, we have excluded all measurements with solar zenith angle (SZA) greater
than $`r 90 - BIO_ELEVA`^\circ$.  Finally, images from a sky camera have been used in
the manual inspection of the CE events identification. The sky camera has been
operating since 2012 and stores images in 15 min time steps.  An overview of the GHI
data used in this study is given in Figure\nobreakspace{}\ref{fig:CLB-daily}, as the
daily means.  Daily means were calculated only for days with at least $60\,\%$ of
data availability; however, all available one-minute measurements have been used for
the detection of CE events.

>>>>

<!-- Radiation data quality check -->
To further improve the quality of the irradiance data, a manual screening was
performed, to remove inconsistent and erroneous recordings that can occur
stochastically or systematically during the long operation of the instrument.  The
manual screening was aided by a radiation data quality assurance procedure, adjusted
for the site, which was based on the methods of Long and Shi\ [-@Long2006;
-@Long2008a].  Thus, problematic recordings have been excluded from further
processing.  Furthermore, due to the significant measurement uncertainty in GHI when
the Sun is near the horizon, and due to some systematic obstructions by nearby
buildings, we have excluded all measurements with solar zenith angle (SZA) greater
than $`r 90 - BIO_ELEVA`^\circ$.  Finally, images from a sky camera have been used in
the manual inspection of the CE events identification. The sky camera has been
operating since 2012 and stores images in 15 min time steps.  An overview of the GHI
data used in this study is given in Figure\nobreakspace{}\ref{fig:CLB-daily}, as the
daily means.  Daily means were calculated only for days with at least $60\,\%$ of
data availability; however, all available one-minute measurements have been used for
the detection of CE events.
